---
title: "How to run MOSAIC"
author: Arshi Arora^[arshiaurora@gmail.com]
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to run MOSAIC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```

In this package we provide the following datasets: 

1. `cv.stats`: This .Rdata object is the output of MOSAIC after running it for 50 rounds of 5-fold cross validation for all 13 - RNA data, 6 DNA Methylation and 6 DNA Accessibility data types. 

2. `solnk`: .Rdata object summarizing the cross validated solution for each data type, picked after comparing their `Adjusted Mutual Information (AMI)` and `Standardized Pooled Within Sum of Squares (SPWSS)` with the outcome of interest. 

For scNMT seq data, MOSAIC was run as follows: 

```{r, eval=FALSE}

bigK = 7
library(doParallel)
registerDoParallel(cores=bigK)

library(MOSAIC)

load("stage.rmVisceralEnd.Rdata")
load("rna.mat.Rdata")

mat<-list(); mat[[1]] =x[names(stage),]

cvrounds<-function(x,out,kk){
    this.fold=5
    fit<-list()
    for (i in 1:50){
        fit[[i]] = cv.mosaic(x, out,kk,this.fold)

    }
    print(paste0("finished ", this.fold, " rounds for k= ", kk))
    return(fit)
}

cv.fit<-foreach(kk=2:bigK) %dopar% cvrounds(mat,stage,kk)

```